%!TEX root = ../article.tex

% Abstract
\begin{abstract}
With the rapid develoment of cloud platform,the fault diagnosis for cloud platform becomes a hot research area. Although centralized management is applied for cloud platform, the size of which is still increasing, more and more components are added to the platform, which make the system difficult to diagnosis fault when fault happens. In this paper, we proposed an framework in order to facilitate the fault diagnosis of OpenStack which is currently a popular cloud platform. Fault localization techniques are used to analyse the root cause of the system failures. Event log has been widely used in fault localization techniques. Two ways are mainly adopted to localize a fault,the first is using fault model to identify a known fault;the second is using normal  behaviour model to identify the abnormal behaviour. However, due to the complexity of the cloud platform, it is still of great challenge for troubleshooting or pinpoint a fault in massive event log data.In this paper, we try to construct a log repository by collecting logs from OpenStack .During the process, some algorithms are presented for log classification, log analysis and fault log correlation analysis.
Meanwhile, we build a knowledge base repository by collecting some troubleshooting question and answers (QA) topic related to OpenStack from the famous QA websites with web crawling technology, and then propose a general automatic approach to pinpoint logs of fault from log files of open cloud platform. 
\end{abstract}